基于卷积神经网络的视觉目标跟踪算法研究

### 2021-09-27 博士/毕业论文/ucasthesis/Tex/Chap_IGCF.tex
CF2和CCOT引用重复

大多数基于 DCF 的跟踪器仅限于使用单分辨率特征图，从而极大地限制了其潜力。为了解决此问题，CCOT 跟踪器 \cite{CCOT} 学习连续卷积滤波器以融合以不同分辨率获得的特征图。这将为目标生成连续域置信度图。除了多分辨率融合之外，连续域学习公式还可以实现精确的亚像素定位。
ECO 跟踪器 \cite{danelljan2017eco} 在 DCF 公式中引入分解卷积算子训练样本分布的紧凑生成模型，并采用保守的模型更新策略。ECO 使用了 CNN 特征，同时减轻了计算开销。CF2 跟踪器 \cite{Ma2015HierarchicalCF} 自适应地学习每个卷积层上的相关滤波器，以对目标表观进行编码，并使用每一层的相关响应来推断目标位置。

>>>>

大多数基于 DCF 的跟踪器仅限于使用单分辨率特征图，从而极大地限制了其潜力。为了解决此问题，CCOT 跟踪器 \cite{danelljan2016beyond} 学习连续卷积滤波器以融合以不同分辨率获得的特征图。这将为目标生成连续域置信度图。除了多分辨率融合之外，连续域学习公式还可以实现精确的亚像素定位。
ECO 跟踪器 \cite{danelljan2017eco} 在 DCF 公式中引入分解卷积算子训练样本分布的紧凑生成模型，并采用保守的模型更新策略。ECO 使用了 CNN 特征，同时减轻了计算开销。CF2 跟踪器 \cite{CF2} 自适应地学习每个卷积层上的相关滤波器，以对目标表观进行编码，并使用每一层的相关响应来推断目标位置。

### 2021-09-27 博士/毕业论文/ucasthesis/Tex/Chap_MTP.tex
CF2和CCOT引用重复

\textbf{GOT-10k} 我们将平均重叠（AO）分数用作 GOT-10k \cite{GOT-10k} 的性能指标。我们将本章提出的方法与 CF2 \cite{CF2}，ECO \cite{danelljan2017eco}，CCOT \cite{CCOT}，GOTURN \cite{GOTURN}，SiamFC \cite{SiamFC}，SiamFCv2 \cite{valmadre2017end}，ATOM \cite{danelljan2019atom}，SiamFC++\_AlexNet \cite{SiamFC++} 和 SiamFC++
\_GoogLeNet \cite{SiamFC++} 在该数据库上进行比较。模板更新的迭代次数设置为 2。在图 \ref{fig:got10k} 中可以发现，与列出的跟踪器相比，本章提出的算法具有更好的跟踪性能。

>>>>

\textbf{GOT-10k} 我们将平均重叠（AO）分数用作 GOT-10k \cite{GOT-10k} 的性能指标。我们将本章提出的方法与 CF2 \cite{CF2}，ECO \cite{danelljan2017eco}，CCOT \cite{danelljan2016beyond}，GOTURN \cite{GOTURN}，SiamFC \cite{SiamFC}，SiamFCv2 \cite{valmadre2017end}，ATOM \cite{danelljan2019atom}，SiamFC++\_AlexNet \cite{SiamFC++} 和 SiamFC++
\_GoogLeNet \cite{SiamFC++} 在该数据库上进行比较。模板更新的迭代次数设置为 2。在图 \ref{fig:got10k} 中可以发现，与列出的跟踪器相比，本章提出的算法具有更好的跟踪性能。

### 2021-09-27 博士/毕业论文/ucasthesis/Tex/Chap_end.tex
CF2和CCOT引用重复

%本章提出的网络在 GOT-10k \cite{GOT-10k} 的训练集上进行训练，而主干网络在 ImageNet 上进行了预训练。
%我们应用动量​​为 0.9 的随机梯度下降作为优化方法，并将权重衰减设置为 0.0005。
%学习率从 $10^{-2}$ 降至 $10^{-4}$。
%批次大小设置为 2，并对网络进行了 90000 次迭代训练。
%本章提出的跟踪器是使用 PyTorch 在 Python 中实现的。
%First stage, we select 4000 proposals to send to stage2, the positive/negative rate is 1:3.
%To shift channels $K=2$.
%Because of the memory limit, the batch size is 2.
%To calculate the loss, $\lambda = 1$.
%For both training and testing, the size of a template image is 
% 其实有些对不上。按论文上讲，第一阶段是找到若干候选框。第二阶段是得到唯一结果。实际上是，第一阶段得到若干候选框，第二阶段进一步筛选得到约10个候选框（这才是真正的相似目标），然后按IoU和得分来选择最终结果。
% For test, we select top 100 proposals to send to stage2. The we use NMS to select top 10 object. 
\subsection{基于数据集 GOT-10k 的评测结果分析}
\begin{table}[t]
\centering
\caption{本章提出的跟踪算法与相关算法在 GOT-10k \cite{GOT-10k} 测试集上的评测结果。}
\begin{tabular}{l l l l}
\bottomrule
跟踪器   &  AO   &  $\textbf{SR}_{0.50}$ & $\textbf{SR}_{0.75}$  \\
\hline
本章算法 &  $\textbf{0.577}^\textbf{1}$ & $\textbf{0.662}^\textbf{1}$  & $\textbf{0.509}^\textbf{1}$  \\
SiamMask \cite{Wang2018SiamMask} &  0.459&  0.560 &0.205 \\
SiamFCv2 \cite{valmadre2017end} &  0.374&  0.404 &0.144 \\
SiamFC \cite{SiamFC}  &  0.348&  0.353 &0.098 \\
GOTURN \cite{GOTURN} &  0.347&  0.375 &0.124 \\
CCOT	 \cite{CCOT} &  0.325&  0.328 &0.107 \\
ECO \cite{danelljan2017eco} &  0.316&  0.309 &0.111 \\
CF2 \cite{CF2} &  0.315&  0.297 &0.088 \\
MDNet \cite{MDNet} &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:end_got10k}
\end{table}
在本节中，我们在 GOT-10k \cite{GOT-10k} 数据集上评估本章提出的算法。
% Say something about this dataset.
GOT-10k 是最近提出的目标跟踪数据集，包含超过 10000 个视频序列，目标由矩形边界框注释。
%Note that the classes between training and test sets are zero-overlapped. 
%This one-shot protocol avoids the evaluation bias towards familiar objects. 
GOT-10k 测试集包括 180 段视频序列，具有 84 种不同的目标类别和 32 种运动模式。我们使用文献 \cite{GOT-10k} 中提出的平均重叠（AO）分数和成功率（SR）作为性能指标。AO 表示所有真实边界框和估计边界框之间重叠的平均值，而 SR 表示重叠超过 0.5/0.75 的成功跟踪帧的百分比。

>>>>

%本章提出的网络在 GOT-10k \cite{GOT-10k} 的训练集上进行训练，而主干网络在 ImageNet 上进行了预训练。
%我们应用动量​​为 0.9 的随机梯度下降作为优化方法，并将权重衰减设置为 0.0005。
%学习率从 $10^{-2}$ 降至 $10^{-4}$。
%批次大小设置为 2，并对网络进行了 90000 次迭代训练。
%本章提出的跟踪器是使用 PyTorch 在 Python 中实现的。
%First stage, we select 4000 proposals to send to stage2, the positive/negative rate is 1:3.
%To shift channels $K=2$.
%Because of the memory limit, the batch size is 2.
%To calculate the loss, $\lambda = 1$.
%For both training and testing, the size of a template image is 
% 其实有些对不上。按论文上讲，第一阶段是找到若干候选框。第二阶段是得到唯一结果。实际上是，第一阶段得到若干候选框，第二阶段进一步筛选得到约10个候选框（这才是真正的相似目标），然后按IoU和得分来选择最终结果。
% For test, we select top 100 proposals to send to stage2. The we use NMS to select top 10 object. 
\subsection{基于数据集 GOT-10k 的评测结果分析}
\begin{table}[t]
\centering
\caption{本章提出的跟踪算法与相关算法在 GOT-10k \cite{GOT-10k} 测试集上的评测结果。}
\begin{tabular}{l l l l}
\bottomrule
跟踪器   &  AO   &  $\textbf{SR}_{0.50}$ & $\textbf{SR}_{0.75}$  \\
\hline
本章算法 &  $\textbf{0.577}^\textbf{1}$ & $\textbf{0.662}^\textbf{1}$  & $\textbf{0.509}^\textbf{1}$  \\
SiamMask \cite{Wang2018SiamMask} &  0.459&  0.560 &0.205 \\
SiamFCv2 \cite{valmadre2017end} &  0.374&  0.404 &0.144 \\
SiamFC \cite{SiamFC}  &  0.348&  0.353 &0.098 \\
GOTURN \cite{GOTURN} &  0.347&  0.375 &0.124 \\
CCOT	 \cite{danelljan2016beyond} &  0.325&  0.328 &0.107 \\
ECO \cite{danelljan2017eco} &  0.316&  0.309 &0.111 \\
CF2 \cite{CF2} &  0.315&  0.297 &0.088 \\
MDNet \cite{MDNet} &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:end_got10k}
\end{table}
在本节中，我们在 GOT-10k \cite{GOT-10k} 数据集上评估本章提出的算法。
% Say something about this dataset.
GOT-10k 是最近提出的目标跟踪数据集，包含超过 10000 个视频序列，目标由矩形边界框注释。
%Note that the classes between training and test sets are zero-overlapped. 
%This one-shot protocol avoids the evaluation bias towards familiar objects. 
GOT-10k 测试集包括 180 段视频序列，具有 84 种不同的目标类别和 32 种运动模式。我们使用文献 \cite{GOT-10k} 中提出的平均重叠（AO）分数和成功率（SR）作为性能指标。AO 表示所有真实边界框和估计边界框之间重叠的平均值，而 SR 表示重叠超过 0.5/0.75 的成功跟踪帧的百分比。

### 2021-09-27 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
CF2和CCOT引用重复

\begin{table}[t]
\centering
\caption{将本章提出的方法与其他视觉目标跟踪方法在 GOT-10k 测试集上的跟踪结果进行比较。跟踪器按其平均重叠率（AO）排名。}
\begin{tabular}{cccc}
\bottomrule
Method   &  AO   &  SR$_{0.50}$ & SR$_{0.75}$  \\
\hline
Ours &  $\textbf{0.560}^\textbf{1}$ & $\textbf{0.645}^\textbf{1}$  & $\textbf{0.457}^\textbf{1}$  \\
SiamMask &  0.459&  0.560 &0.205 \\
SiamFCv2 &  0.374&  0.404 &0.144 \\
SiamFC   &  0.348&  0.353 &0.098 \\
GOTURN	 &  0.347&  0.375 &0.124 \\
CCOT	 &  0.325&  0.328 &0.107 \\
ECO	     &  0.316&  0.309 &0.111 \\
CF2	     &  0.315&  0.297 &0.088 \\
MDNet	 &  0.299&  0.303 &0.099 \\
CFNetc2	 &  0.293&  0.265 &0.087 \\
ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}

>>>>

\begin{table}[t]
\centering
\caption{将本章提出的方法与其他视觉目标跟踪方法在 GOT-10k 测试集上的跟踪结果进行比较。跟踪器按其平均重叠率（AO）排名。}
\begin{tabular}{cccc}
\bottomrule
跟踪器   &  AO   &  SR$_{0.50}$ & SR$_{0.75}$  \\
\hline
本章算法 &  $\textbf{0.560}^\textbf{1}$ & $\textbf{0.645}^\textbf{1}$  & $\textbf{0.457}^\textbf{1}$  \\
SiamMask \cite{Wang2018SiamMask}  &  0.459&  0.560 &0.205 \\
SiamFCv2 \cite{valmadre2017end} &  0.374&  0.404 &0.144 \\
SiamFC \cite{SiamFC} &  0.348&  0.353 &0.098 \\
GOTURN	\cite{GOTURN} &  0.347&  0.375 &0.124 \\
CCOT	 \cite{danelljan2016beyond} &  0.325&  0.328 &0.107 \\
ECO \cite{danelljan2017eco} &  0.316&  0.309 &0.111 \\
CF2	\cite{CF2} &  0.315&  0.297 &0.088 \\
MDNet \cite{MDNet} &  0.299&  0.303 &0.099 \\
CFNetc2 \cite{valmadre2017end} &  0.293&  0.265 &0.087 \\
ECOhc \cite{danelljan2017eco} &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}

### 2021-09-27 博士/毕业论文/ucasthesis/Tex/english/Chap_IGCF_english.tex
CF2和CCOT引用重复

Most DCF-based trackers are restricted to single-resolution feature maps, significantly limiting their potential. To solve this problem, the CCOT tracker \cite{CCOT} learns continuous convolution filters to fuse the feature maps obtained at different resolutions. This produces a continuous-domain confidence map for the target. In addition to multi-resolution fusion, the continuous domain learning formulation enables accurate sub-pixel localization.
The ECO tracker \cite{Danelljan2017ECOEC} includes in the core DCF formulation a factorized convolution operator, a compact generative model of the training sample distribution and a conservative model update strategy. This alleviates the computational overhead due to the use of CNN features. In contrast, the CF2 tracker \cite{Ma2015HierarchicalCF} adaptively learns correlation filters on each convolutional layer to encode the target appearance and infers the target location using the correlation response of each layer.

>>>>

Most DCF-based trackers are restricted to single-resolution feature maps, significantly limiting their potential. To solve this problem, the CCOT tracker \cite{danelljan2016beyond} learns continuous convolution filters to fuse the feature maps obtained at different resolutions. This produces a continuous-domain confidence map for the target. In addition to multi-resolution fusion, the continuous domain learning formulation enables accurate sub-pixel localization.
The ECO tracker \cite{Danelljan2017ECOEC} includes in the core DCF formulation a factorized convolution operator, a compact generative model of the training sample distribution and a conservative model update strategy. This alleviates the computational overhead due to the use of CNN features. In contrast, the CF2 tracker \cite{Ma2015HierarchicalCF} adaptively learns correlation filters on each convolutional layer to encode the target appearance and infers the target location using the correlation response of each layer.

### 2021-09-27 博士/毕业论文/ucasthesis/Tex/english/Chap_MTP_english.tex
CF2和CCOT引用重复

\textbf{GOT-10k} We use the average overlap (AO) score as performance measure following \cite{GOT-10k}. We compare our method with CF2 \cite{CF2}, ECO \cite{danelljan2017eco}, CCOT \cite{CCOT}, GOTURN \cite{GOTURN}, SiamFC \cite{SiamFC}, SiamFCv2 \cite{valmadre2017end}, ATOM \cite{danelljan2019atom}, SiamFC++\_AlexNet \cite{SiamFC++} and SiamFC++\_GoogLeNet \cite{SiamFC++} on this dataset. The iteration number for template update is set to 2. In Fig. \ref{fig:got10k}, we can find that the proposed algorithm achieves better tracking performance compared with the listed state-of-the-art trackers.

>>>>

\textbf{GOT-10k} We use the average overlap (AO) score as performance measure following \cite{GOT-10k}. We compare our method with CF2 \cite{CF2}, ECO \cite{danelljan2017eco}, CCOT \cite{danelljan2016beyond}, GOTURN \cite{GOTURN}, SiamFC \cite{SiamFC}, SiamFCv2 \cite{valmadre2017end}, ATOM \cite{danelljan2019atom}, SiamFC++\_AlexNet \cite{SiamFC++} and SiamFC++\_GoogLeNet \cite{SiamFC++} on this dataset. The iteration number for template update is set to 2. In Fig. \ref{fig:got10k}, we can find that the proposed algorithm achieves better tracking performance compared with the listed state-of-the-art trackers.
